Machine Learning Autoencoder Applied to Communication Channels

### 2019-06-20 Rapport/Article/Article.tex
Seance 06/20/2019

The architecture of the DNN necessary to achieve a great performance in terms of BER is not evident. What should be remarked though is the first layer of the DNN. A \textit{Lambda} layer is a layer in which the activation operations are user defined and the parameters are non-trainable. Thus, we were able to define a layer that act as a BSC to force our DNN to learn its effects in the training data. The fact that the parameters are non-trainable means that the noise layer is applied in forward propagation only.

@@

Despite of this, an encoding matrix is still needed. A commonly used method in ML for image recognition without training labels is the autoencoder. In this context, the NN is able to learn not only a decoding algorithm, but also a decoding one as introduced in the following section.

@@

Briefly state that it is basically the same, apart from the input and output layers AND it demands a tremendously different architecture.

@@

 \multirow{2}{*}{Decoder} & Dense: 128, input size: 16 \\
 & Dense: 256, activation: Sigmoid  \\ \hline

@@

\begin{table}
\caption{Decoding time comparison between the MAP algorithm and the DNN decoders and autoencoders. The data is normalized to the mean MAP algorithm decoding time. } 
\begin{center}

@@

Talk about feasibility of decoders, improved performance of the channel delay with DNN decoders, challenges in implementing this architecture in real life, challenges in training the NNs, Future work, what else could be done with NN in error correction,

>>>>

The architecture of the DNN necessary to achieve a great performance in terms of BER is not evident. To begin we must define which layers were used and why. A \textit{Lambda} layer is a layer in which the activation function is user defined and the parameters are non-trainable. Thus, we were able to define a layer that act as a BSC to force our DNN to learn its effects in the training data. The fact that the parameters are non-trainable means that the noise layer is applied in forward propagation only. A Dense layer is a densely connected layer, which means that each neuron receives input from all the neurons in the previous layer. Thus it is often used to change the dimensions of a vector. In other words, it applies a rotation, scaling and translation transform to a vector as shown in equation \ref{eq:eqFP}. The values in the weight matrix are trainable parameters which are updated during BP \cite{chollet2015keras}.

@@

Even though DNN encoders are useful, an encoding matrix is still needed. With a view to eliminate completely the need of an explicit encoding, a technique commonly used method in ML for image recognition is explored. The autoencoder is able to learn not only a decoding algorithm, but also a decoding one as introduced in the following section.

@@

Briefly state that it is basically the same, apart from the input and output layers AND it demands a tremendously different architecture, batch normalization.

@@

 \multirow{2}{*}{Decoder} & Dense: 128, input size: 16 \\
 & Dense: 256, activation: Softmax  \\ \hline

@@

\begin{table}
\caption{Decoding time comparison between the MAP algorithm and the DNN decoders and autoencoders. The data is normalized to the average MAP algorithm decoding time. } 
\begin{center}

@@

Talk about feasibility of decoders, improved performance of the channel delay with DNN decoders, challenges in implementing this architecture in real life, challenges in training the NNs, Future work, what else could be done with NN in error correction, Advantages and disadvantages in comparison with linear decoding.
